### 2015-01-13 Paper_Markdown.Rmd
Mostly text and mapping changes to the Paper_Markdown.Rmd` file. * Moved "shared" run files to the `shared run` folder to provide a clean folder with just the bootstrap code. * Moved a few files to the `deprecated` folder. * Made sure to explicitly call the `rioja` version of `performance` in the WAPLS code.

Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================

@@

for(i in 1:ncol(clim)){
  test.struct <- rda(pol ~ clim[,i])
  clim.ratio[i] <- test.struct$CCA$tot.chi / test.struct$CA$tot.chi
}

@@

na.samples <- data.frame(site = rep(climate[,1], ncol(mat.res$bias)),
                         size = as.vector(mat.res$sample_size),
                         distance = rep(seq(0, 1, by=0.01), each = nrow(mat.res$sample_size)))

@@

loss <- ggplot(na.samples, aes(x=distance, y=size)) + 
  geom_path(aes(group=site), alpha=0.01) +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme_bw() +
  theme(text = element_text(size=24, family='serif'),
        axis.text = element_text(size=14, family='serif')) +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  geom_segment(aes(x=0.48, xend = 0.48, y = min(mat.res$sample_size, na.rm=TRUE), yend = nrow(climate)), size=1, color='red', linetype=2)

loc.loss <- data.frame(lat =  climate$LATDD,
                       long = climate$LONDD,
                       loss = 1 - mat.res$sample_size[,49] / nrow(climate))

loss.map <-  ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_path(aes(group=group), color='black') +
  geom_point(data = loc.loss, 
             aes(x = long, y = lat, color = loss), alpha=0.5) +
   theme_bw() +
  theme(text = element_text(size=24, family='serif'),
        axis.text = element_text(size=14, family='serif')) +
  coord_map(projection='albers', lat0=30, lat1=50, xlim=c(-140, -60), ylim=c(26, 75)) +
  scale_color_continuous(low = '#F08080', high='#4169E1') +
  xlab('') + ylab('')

@@

>>>>

---
output: word_document
---
Non-analogues in paleoecological reconstruction - the effects of analogue distance
========================================================

@@

for(i in 1:ncol(clim)){
  test.struct <- rda(pol ~ clim[,i], na.action = na.omit)
  clim.ratio[i] <- test.struct$CCA$tot.chi / test.struct$CA$tot.chi
}

@@

point.loss <- 1 - mat.res$sample_size[,49] / nrow(climate)

na.samples <- data.frame(site = rep(climate[,1], ncol(mat.res$bias)),
                         lat = rep(climate$LATDD, ncol(mat.res$bias)),
                         long = rep(climate$LONDD, ncol(mat.res$bias)),
                         loss = point.loss,
                         bin = factor(round(ecdf(point.loss)(point.loss), 1)),
                         size = as.vector(mat.res$sample_size),
                         distance = rep(seq(0, 1, by=0.01), each = nrow(mat.res$sample_size)))

@@

loss <- ggplot(data = na.samples, aes(x=distance, y=size)) + 
  geom_path(aes(group=site, color = bin)) +
  scale_color_brewer(palette = 'PiYG', type = 'div') +
  xlab('Analogue Distance') + ylab('Available Samples') +
  theme(text = element_text(size=24, family='serif'),
        axis.text = element_text(size=14, family='serif'),
        legend.position = 'none') +
  scale_x_continuous(expand = c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  geom_segment(aes(x=0.48, 
                   xend = 0.48, 
                   y = min(mat.res$sample_size, na.rm=TRUE), 
                   yend = nrow(climate)), 
               size=1, color='red', linetype=2)

loc.loss <- data.frame(lat =  climate$LATDD,
                       long = climate$LONDD,
                       loss = point.loss,
                       bin  = factor(round(ecdf(point.loss)(point.loss), 1)))

loss.map <-  ggplot(data = data.frame(map), aes(long, lat)) + 
  geom_polygon(aes(group=group), color='blue', alpha=0.2) +
  geom_point(data = loc.loss, 
             aes(x = long, y = lat, color = bin), alpha=0.7, size = 3) +
  theme_bw() +
  xlab('Longitude') + ylab('Latitude') +
  theme(axis.text=element_text(size=12, family='serif'),
        panel.background = element_rect(fill = 'lightblue'),
        legend.position = 'none') +
  coord_map(projection='albers', lat0=35, lat1=55, xlim=c(-100, -60), ylim=c(35, 80)) +
  scale_color_brewer(palette = 'PiYG', type = 'div')
  #scale_color_continuous(low = '#F08080', high='#4169E1')

@@

We have an interesting distribution of loss here.  First, the color coding is based on loss to 'non-analogue' conditions, and we see that it is possible for some samples to have relatively low loss to the no-analogue point, but then much higher losses to the extreme end of our analogue space (see the magenta lines at the very bottom end of Figure 4a.).  Secondly, the points that lose the most samples tend to be in the boreal forest.  To some degree this is surprising, however, the dominance of Pinus and Picea in these forests likely means that they have smaller analogue distances from one another than samples in the southern forests (with more diversity and therfore, likely fewer close analogues), but also, surpisingly, arctic samples also have higer inter-sample distances, and are thus less sensitive to losses of close analogues.
